\documentclass[11pt,a4paper]{article}

\usepackage[top=1in,bottom=1in,left=1.1in,right=1.1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{parskip}
\usepackage[table]{xcolor}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{mdframed}
\usepackage{enumitem}
\usepackage{listings}

% ── Colours ──────────────────────────────────────────────────────────────────
\definecolor{navy}{RGB}{15, 52, 96}
\definecolor{accent}{RGB}{0, 150, 190}
\definecolor{lightbg}{RGB}{245, 248, 252}
\definecolor{codebg}{RGB}{30, 35, 50}
\definecolor{codetext}{RGB}{200, 220, 255}
\definecolor{rowalt}{RGB}{237, 243, 250}
\definecolor{muted}{RGB}{100, 110, 130}
\definecolor{green}{RGB}{40, 160, 80}
\definecolor{orange}{RGB}{200, 100, 20}
\definecolor{rulecol}{RGB}{200, 220, 235}
\definecolor{warnyellow}{RGB}{255, 248, 235}

% ── Hyperlinks ────────────────────────────────────────────────────────────────
\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=navy,
  pdftitle={Aion — Installation Guide}}

% ── Section headings ─────────────────────────────────────────────────────────
\titleformat{\section}
  {\Large\bfseries\color{navy}}{}{0em}{}
  [\vspace{2pt}\color{accent}\hrule height 1.5pt\vspace{4pt}]
\titleformat{\subsection}{\normalsize\bfseries\color{accent}}{}{0em}{}
\titlespacing{\section}{0pt}{18pt}{6pt}
\titlespacing{\subsection}{0pt}{10pt}{4pt}

% ── Header / Footer ───────────────────────────────────────────────────────────
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[L]{\small\color{muted}Aion — Installation Guide}
\fancyhead[R]{\small\color{muted}github.com/draygen/aion}
\fancyfoot[C]{\small\color{muted}\thepage}

% ── Code blocks ───────────────────────────────────────────────────────────────
\lstdefinestyle{shell}{
  backgroundcolor=\color{codebg},
  basicstyle=\ttfamily\small\color{codetext},
  breaklines=true,
  breakatwhitespace=true,
  frame=none,
  xleftmargin=10pt, xrightmargin=10pt,
  aboveskip=6pt, belowskip=6pt,
  showstringspaces=false,
  moredelim=[is][\color{green}]{@}{@},
  moredelim=[is][\color{orange}]{!}{!},
}
\lstset{style=shell}

% ── Callout boxes ─────────────────────────────────────────────────────────────
\newmdenv[backgroundcolor=lightbg, linecolor=accent, linewidth=2pt,
  leftline=true, rightline=false, topline=false, bottomline=false,
  innerleftmargin=10pt, innerrightmargin=8pt,
  innertopmargin=6pt, innerbottommargin=6pt,
  skipabove=8pt, skipbelow=8pt]{infobox}

\newmdenv[backgroundcolor=warnyellow, linecolor=orange, linewidth=2pt,
  leftline=true, rightline=false, topline=false, bottomline=false,
  innerleftmargin=10pt, innerrightmargin=8pt,
  innertopmargin=6pt, innerbottommargin=6pt,
  skipabove=8pt, skipbelow=8pt]{warnbox}

% ── Helpers ───────────────────────────────────────────────────────────────────
\newcommand{\code}[1]{{\ttfamily\small\color{navy}#1}}
\newcolumntype{M}[1]{>{\raggedright\arraybackslash}p{#1}}
\renewcommand{\arraystretch}{1.35}

% step counter
\newcounter{step}
\newcommand{\step}[1]{%
  \stepcounter{step}%
  \subsection*{\colorbox{navy}{\color{white}\;\textbf{Step \thestep}\;}\quad #1}%
}

% ─────────────────────────────────────────────────────────────────────────────
\begin{document}

% ── Title block ───────────────────────────────────────────────────────────────
\begin{center}
  {\fontsize{28}{34}\selectfont\bfseries\color{navy} AION}\\[4pt]
  {\large\color{muted} Installation Guide}\\[6pt]
  {\small\color{muted}
    \href{https://github.com/draygen/aion}{github.com/draygen/aion}}
\end{center}
\vspace{4pt}
\noindent\color{accent}\hrule height 2pt
\vspace{14pt}

% ── Prerequisites ─────────────────────────────────────────────────────────────
\section{Prerequisites}

Before you start, make sure the following are installed on your machine.

\vspace{6pt}
\begin{tabularx}{\linewidth}{M{3.2cm} M{2.8cm} X}
  \toprule
  \rowcolor{navy}
  \color{white}\textbf{Requirement} & \color{white}\textbf{Min Version} & \color{white}\textbf{Install} \\
  \midrule
  \rowcolor{rowalt}
  Python        & 3.10+  & \href{https://python.org}{python.org} \\
  Git           & any    & \href{https://git-scm.com}{git-scm.com} \\
  \rowcolor{rowalt}
  Ollama        & latest & \href{https://ollama.com}{ollama.com} \\
  \bottomrule
\end{tabularx}

\begin{infobox}
  \textbf{Platform notes:}
  These instructions work on \textbf{Linux}, \textbf{macOS}, and \textbf{Windows WSL2}.
  Native Windows (CMD/PowerShell) is not supported — use WSL2.
\end{infobox}

% ── Steps ─────────────────────────────────────────────────────────────────────
\section{Setup}

% Step 1
\step{Clone the repository}

\begin{lstlisting}
git clone https://github.com/draygen/aion.git
cd aion
\end{lstlisting}

% Step 2
\step{Create a Python virtual environment}

\begin{lstlisting}
python3 -m venv .venv
source .venv/bin/activate
\end{lstlisting}

You should see \code{(.venv)} at the start of your terminal prompt.

% Step 3
\step{Install Python dependencies}

\begin{lstlisting}
pip install -r requirements.txt
\end{lstlisting}

This installs Flask, scikit-learn, bcrypt, gunicorn, and all other required packages.

% Step 4
\step{Create your local config file}

Aion keeps secrets out of git using a \code{config\_local.py} file that you create yourself.
Copy the template and fill in your values:

\begin{lstlisting}
cp config_local.py config_local.py.bak  # optional backup
\end{lstlisting}

Open \code{config\_local.py} in any editor and set:

\begin{lstlisting}
CONFIG_LOCAL = {
    "elevenlabs_api_key": "",   # optional - for voice output
    "vast_api_key":        "",   # optional - for cloud deployment
    "admin_key":    "pick-a-secret",   # protects the /logs page
    "admin_password": "pick-a-password",  # Brian's login password
}
\end{lstlisting}

\begin{warnbox}
  \textbf{Important:} \code{config\_local.py} is gitignored and will never be committed.
  Do not put secrets in \code{config.py} — that file is public.
\end{warnbox}

% Step 5
\step{Start Ollama and pull the LLM model}

In a separate terminal (or run in the background):

\begin{lstlisting}
ollama serve
\end{lstlisting}

Then pull the model Aion uses (this downloads \textasciitilde4GB — one time only):

\begin{lstlisting}
ollama pull qwen2.5:7b
\end{lstlisting}

Wait until the pull completes before continuing.

% Step 6
\step{Create the data directory}

The \code{data/} folder is gitignored so it won't exist after a fresh clone.
Create it manually:

\begin{lstlisting}
mkdir -p data
\end{lstlisting}

Aion will auto-create \code{data/aion.db} (users, history) and
\code{data/shared\_learned.jsonl} (learned facts) on first run.

% Step 7
\step{Start Aion}

\textbf{Development mode} (auto-reloads on code changes):
\begin{lstlisting}
.venv/bin/python web.py
\end{lstlisting}

\textbf{Production mode} (stable, recommended):
\begin{lstlisting}
.venv/bin/gunicorn -w 1 -b 0.0.0.0:5000 --timeout 120 web:app
\end{lstlisting}

Open your browser and go to: \quad \href{http://localhost:5000}{\textbf{http://localhost:5000}}

% Step 8
\step{First login}

On first run, Aion automatically creates the admin account:

\vspace{6pt}
\begin{tabularx}{0.5\linewidth}{M{2.8cm} X}
  \toprule
  \rowcolor{navy}\color{white}\textbf{Field} & \color{white}\textbf{Value} \\
  \midrule
  \rowcolor{rowalt} Username & \code{brian} \\
  Password & whatever you set as \code{admin\_password} in Step 4 \\
  \bottomrule
\end{tabularx}

\vspace{8pt}
After logging in you will see the chat interface. Admin users also have access
to the \textbf{Admin} panel in the top-right corner.

% ── Adding more users ─────────────────────────────────────────────────────────
\section{Adding More Users}

Once logged in as admin, create additional users via the API:

\begin{lstlisting}
curl -X POST http://localhost:5000/api/admin/users \
  -H "Content-Type: application/json" \
  -b cookies.txt \
  -d '{"username": "gary", "password": "garyspassword", "role": "user"}'
\end{lstlisting}

Or use the \code{/admin} panel in the browser once the Vast.ai section is set up.

% ── Optional: TTS ─────────────────────────────────────────────────────────────
\section{Optional: Voice Output (ElevenLabs TTS)}

Aion supports text-to-speech via ElevenLabs. To enable it:

\begin{enumerate}[leftmargin=1.4em, itemsep=2pt]
  \item Get an API key from \href{https://elevenlabs.io}{elevenlabs.io}
  \item Add it to \code{config\_local.py}: \code{"elevenlabs\_api\_key": "your-key"}
  \item The TTS ON/OFF toggle in the chat UI will now produce audio
\end{enumerate}

% ── Optional: Vast.ai ─────────────────────────────────────────────────────────
\section{Optional: Cloud Deployment (Vast.ai)}

To use the admin GPU deployment panel:

\begin{enumerate}[leftmargin=1.4em, itemsep=2pt]
  \item Create an account at \href{https://vast.ai}{vast.ai}
  \item Copy your API key from \textbf{console.vast.ai} $\to$ Account $\to$ API Keys
  \item Add it to \code{config\_local.py}: \code{"vast\_api\_key": "your-key"}
  \item Go to \href{http://localhost:5000/admin}{\code{/admin}} $\to$ \textbf{Find GPU Servers}
  \item Filter by price and VRAM, click \textbf{Deploy} on any row
\end{enumerate}

Aion will provision the instance, install Ollama, pull the model, clone the
repo from GitHub, and start itself automatically within a few minutes.

% ── Troubleshooting ───────────────────────────────────────────────────────────
\section{Troubleshooting}

\begin{tabularx}{\linewidth}{M{4.8cm} X}
  \toprule
  \rowcolor{navy}\color{white}\textbf{Problem} & \color{white}\textbf{Fix} \\
  \midrule
  \rowcolor{rowalt}
  \textit{Ollama not running} &
    Run \code{ollama serve} in a separate terminal. \\

  \textit{Model not found} &
    Run \code{ollama pull qwen2.5:7b} and wait for it to finish. \\

  \rowcolor{rowalt}
  \textit{Login fails on first run} &
    Check \code{admin\_password} is set in \code{config\_local.py}. \\

  \textit{Port 5000 already in use} &
    Run \code{lsof -i :5000} to find the process and kill it,
    or change the port in the \code{gunicorn} command. \\

  \rowcolor{rowalt}
  \textit{Script won't run on WSL} &
    Run \code{sed -i 's/\textbackslash r//' script.sh} to fix Windows
    line endings (CRLF). \\

  \textit{\code{config\_local.py} not found} &
    Create it manually — see Step 4. It is intentionally excluded from git. \\
  \bottomrule
\end{tabularx}

% ── Footer ────────────────────────────────────────────────────────────────────
\vspace{20pt}
\noindent\color{rulecol}\hrule
\vspace{8pt}
{\small\color{muted}\textit{Aion by Brian Wallace \quad — \quad
\href{https://github.com/draygen/aion}{github.com/draygen/aion}}}

\end{document}
